Generating the Blueprints of Java Ecosystem

### 2015-02-22 msr.tex
reorganised tools

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artifacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer \cite{CHKE94} and those presented by Lorenz et al. \cite{LOKI94} that have found their way in software development practice and tools.

@@

Three tools were selected.

@@

Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset. Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics. Several metrics are calculated by more than one tools in this dataset, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}. Both calculation are stored and provided by the dataset.

>>>>

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artifacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer~\cite{CHKE94} and those presented by Lorenz et al.~\cite{LOKI94} that have found their way in software development practice and tools.

@@

Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset. Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics. Several metrics are calculated by more than one tools in this dataset, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}. Both calculation are stored and provided by the dataset. Three tools were selected.

@@
